### 2015-05-19 writing/SNLI paper/corpus.tex
Pre-lunch paper update.

% TODO: Rewrite and expand motivation here (CP?)

@@

% TODO: Rewrite and expand (CP?)

@@

% TODO: Do we need statistics about the number/distribution of workers?
% TODO: Do we need statistics about how much of ImageFlickr we rejected/double-annotated?

@@

The results of this validation process are summarized in Fig.~\ref{validation-stats}. For each pair that we validated, we chose a gold label. If any one of the three labels was chosen by at least three of the five annotators, that label is the gold label. If there was no such consensus, which occurred in about 0.2\% of cases, we chose the label `-'. While these unlabeled examples are included in the corpus distribution, they are unlikely to be helpful for the core classification task of NLI, and we

TODO: Data filtering? Data re-labeling?

@@

% Screenshot from phase 1

% Screenshot from phase 2

The data is freely available at (POST DATA), and is released under a CreativeCommons
Attribution-ShareAlike licence, which is the same licence used for the Flickr30k source captions.

@@

% TODO (CM?)

>>>>

\todo{Rewrite and expand motivation here (CP?)}

@@

\todo{Rewrite and expand (CP?)}

@@

\todo{Do we need statistics about the number/distribution of workers?}
\todo{Do we need statistics about how much of ImageFlickr we rejected/double-annotated?}

@@

The results of this validation process are summarized in Fig.~\ref{validation-stats}. For each pair that we validated, we chose a gold label. If any one of the three labels was chosen by at least three of the five annotators, that label is the gold label. If there was no such consensus, which occurred in about 0.2\% of cases, we chose the label `-'. While these unlabeled examples are included in the corpus distribution, they are unlikely to be helpful for the core classification task of NLI, and we do not include them when training and evaluating the models discussed in later sections.

@@

The data will be released upon publication under a CreativeCommons
Attribution-ShareAlike licence, the same licence used for the Flickr30k source captions.

@@

\todo{Update and expand (CM, SB)}
